### 2014-02-27 paper/relatedwork.tex

Previous work has investigated the integration of interactivity into the fabrication process.  \cite{Willis-printedoptics} used light pipes, solid clear tubes, to create integrated displays.  \cite{Savage-sauron} investigated the use of computer vision to track interactions with physical mechanisms.
\begin{itemize}
\item \cite{Savage-sauron} - Sauron.  computer vision of mechanical components obviates electronics installation.
\item \cite{Willis-infrastructs} - InfraStructs, identification of 3d printed objects using Terahertz imaging
\item \cite{Willis-printedoptics} - Printed Optics.  doing cool stuff with clear material (touch sensing and display)
\item \cite{Slyper-pressure} - robots that are made of squishy stuff where air pressure changes are sensed.  input components designed to react to different manipulations (pushing, squeezing, twisting, etc.)
\item \cite{Navarrette-gps} - I'm a little unclear on what they did, but they fabbed something with a "3D circuitboard" that has a bypass that goes into 3D.  they don't offer a routing algorithm or anything, though.
\end{itemize}

\subsubsection{Printing Electronics}
\begin{itemize}
\item \cite{Sarik-tracebrush} - this uses an airspray machine to add conductive paths to surface of 3D prints
\item \cite{Optomec} - fancy machines that spray conductive film
\item \cite{Sells-reprap} - the RepRap people using a syringe of hot solder to squirt flat circuits into flat channels
\item \cite{icecats-conductivepaint} - an instructable I followed to make my first batch of conductive paint
\end{itemize}

@@

>>>>

Previous work has investigated the integration of interactivity into the fabrication process.  \cite{Willis-printedoptics} used light pipes, solid clear tubes, to create integrated displays.  \cite{Savage-sauron} investigated the use of computer vision to track interactions with physical mechanisms.
\begin{itemize}
\item \cite{Savage-sauron} - Sauron.  computer vision of mechanical components obviates electronics installation.
\item \cite{Willis-printedoptics} - Printed Optics.  doing cool stuff with clear material (touch sensing and display)
\item \cite{Slyper-pressure} - robots that are made of squishy stuff where air pressure changes are sensed.  input components designed to react to different manipulations (pushing, squeezing, twisting, etc.)
\item \cite{Navarrette-gps} - I'm a little unclear on what they did, but they fabbed something with a "3D circuitboard" that has a bypass that goes into 3D.  they don't offer a routing algorithm or anything, though.
\item \cite{Sarik-tracebrush} - this uses an airspray machine to add conductive paths to surface of 3D prints
\item \cite{Optomec} - fancy machines that spray conductive film
\item \cite{Sells-reprap} - the RepRap people using a syringe of hot solder to squirt flat circuits into flat channels
\item \cite{icecats-conductivepaint} - an instructable I followed to make my first batch of conductive paint
\end{itemize}

@@

Our neon routing algorithm is similar to that described by Wong, et al., in \cite{Wong-continuousline}.  However, We are not confined to the plane to avoid line-crossings, and we also have additional freedom in creating lines where none existed.  Because we can shield neon post-print with black tape or material (thus rendering it invisible), we don't have the same need to avoid drawing new line segments, and we are free to create much shorter paths.  It's not quite a TSP
